---
title: "Reproducible Research: Peer Assignment 1"
author: "Victor" 
output: 
  html_document:
    keep_md: true
---
Week 2 Project
===========================
```{r}
activity<-read.csv("C:/data scientist/repro research/week 2/activity.csv")
activity$date<-as.Date(activity$date)
```
1.What is mean total number of steps taken per day?

- Calculate the total number of steps taken per day
```{r}
steps_by_day <- aggregate(steps ~ date, activity, sum)
hist(steps_by_day$steps, main = paste("Total Steps Each Day"), col="blue", xlab="Number of Steps")
rmean<-mean(steps_by_day$steps)
rmedian<-median(steps_by_day$steps)
```
Mean is `r rmean`, median is `r rmedian`
2. What is the average daily activity pattern?
```{r}
steps_by_interval <- aggregate(steps ~ interval, activity, mean)
plot(steps_by_interval$interval,steps_by_interval$steps, type="l", xlab="Interval", ylab="Number of Steps",col = "blue", main="Average Number of Steps per Day by Interval")
max<-max(steps_by_interval$steps)
maxinterval<-steps_by_interval[steps_by_interval$steps==max,1]
```
The `r maxinterval`th 5-minute interval contains the maximum number of steps
3.Imputing missing values
```{r}
incomplete <- sum(!complete.cases(activity))
imputed_data <- transform(activity, steps = ifelse(is.na(activity$steps), steps_by_interval$steps[match(activity$interval, steps_by_interval$interval)], activity$steps))
imputed_data[as.character(imputed_data$date) == "2012-10-01", 1] <- 0
steps_by_day_i <- aggregate(steps ~ date, imputed_data, sum)
hist(steps_by_day_i$steps, main = paste("Total Steps Each Day"), col="blue", xlab="Number of Steps")
#Create Histogram to show difference.
hist(steps_by_day$steps, main = paste("Total Steps Each Day"), col="red", xlab="Number of Steps",add=T)
legend("topright", c("Imputed", "Non-imputed"), col=c("blue", "red"), lwd=10)
meani<-mean(steps_by_day_i$steps)
mediani<-median(steps_by_day_i$steps)
mean_diff <- meani - rmean
med_diff <- mediani - rmedian
```
- Mean is `r meani`, median is `r mediani`

- The difference between the non-imputed mean and imputed mean is `r mean_diff`

- The difference between the non-imputed median and imputed median is `r med_diff`

4.Are there differences in activity patterns between weekdays and weekends?
```{r}
Sys.setlocale(,"ENG")
weekday <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
#is.element to check out if the first parameter is an element of the  sencond.
imputed_data$dow = as.factor(ifelse(is.element(weekdays(as.Date(imputed_data$date)),weekday), "Weekday", "Weekend"))
steps_by_interval_i <- aggregate(steps ~ interval + dow, imputed_data, mean)
library(lattice)
xyplot(steps_by_interval_i$steps ~ steps_by_interval_i$interval|steps_by_interval_i$dow, main="Average Steps per Day by InteInterval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")
```
